%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Web Developer - Remote} % Job title
{\href{http://www.tuinmachines-ello.be/}{Tuinmachines-ello}} % Organization
{Limburg, Belgium} % Location
{Aug. 2018 - Present} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Designing and develop the Frontend Features.}
\item {Identify user and system requirements for new websites and applications.}
\item {Responsible for complete SEO process and web analytics.}
\end{cvitems}
}

\hspace{2em}
%------------------------------------------------    

\cventry
{Web Designer \& SEO Analyst} % Job title
{\href{https://www.fiverr.com/muhammaduzair09}{Fiverr}} % Organization
{Online Marketplace} % Location
{Apr. 2018 - Present} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Create a website layout/user interface by using standard Web practices.}
\item {Gather and refine specifications and requirements based on technical needs}
\item {Building a network of freelance designers and content writers.}
\item {Responsible for maintaining, expanding, and scaling client sites.}
\item { Most Frequently Used CMS: WordPress, Weebly \& Wix}
\end{cvitems}
}

%------------------------------------------------    

\hspace{2em}

\cventry
{Front Desk Admissions Officer - Internship} % Job title
{\href{http://www.nu.edu.pk/}{FAST National University of Computer \& Emerging Sciences}} % Organization
{Peshawar, Pakistan} % Location
{Jul. 2020 - Sep. 2020} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item{Interview students to understand their objectives and background.}
\item {Analyze the applications of prospective students based on standard admission policies.}
\item {Provide clarifications to student’s queries in a professional manner.}
\item{Develop innovative communication strategies, recruitment strategies, and enrolment plans.}
\item{Provide assistance with recruitment activities, student interviews, admission publications, and information sessions.}
\item{Stay plugged into emerging technologies/industry trends and apply them into operations and activities.}
\end{cvitems} 
}

%------------------------------------------------


\end{cventries}