%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Volunteer Work Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Convener} % Affiliation/role
{\href{http://pwr.nu.edu.pk/acm/}{NUCES Peshawar ACM Student Chapter}} % Organization/group
{Peshawar, Pakistan} % Location
{Sep. 2020 - PRESENT} % Date(s)
{ % Description(s) of experience/contributions/knowledge
\begin{cvitems}
\item {Convener provides close liaison between Student Body and Faculty Heads}
\item {Convener has to report ACM Regional Headquarter on monthly basis about ACM activities.}
\item {Any other tasks deemed necessary for the smooth conduct of ACM Activities.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Chairperson} % Affiliation/role
{\href{http://pwr.nu.edu.pk/acm/}{NUCES Peshawar ACM Student Chapter}} % Location
{Aug. 2019 - Sep. 2020} % Date(s)
{ % Description(s) of experience/contributions/knowledge
\begin{cvitems}
\begin{flushleft} \justifying
The chapter Chairperson has the overall responsibility for developing chapter programs, for ensuring that plans and assignments are carried out, and for seeing that the chapter fulfills its obligations to the Association. The Chairperson should be familiar with the policies and procedures of the Association, with the chapter's bylaws, and with the duties of all the other chapter officers and committee chairpersons.
\end{flushleft}
\end{cvitems}
}

%------------------------------------------------
\cventry
{Student Chair} % Affiliation/role
{\href{http://icet.org.pk/2019/}{IEEE 15th International Conference on Emerging Technologies 2019 (ICET'19)}} % Organization/group
{Peshawar, Pakistan} % Location
{Jul. 2020 - Jan. 2020} % Date(s)
{ % Description(s) of experience/contributions/knowledge
\begin{cvitems}
\item {Managing the team of over 100 students and directly reported to ICET Program Chair}
\item{Conduct market research, gather information and negotiate contracts prior to closing any deals.}
\item{Proactively handle any arising issues and troubleshoot any emerging problems on the event day.}
\item {Event planning, design and production while managing all project delivery elements within time limits.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Chief Operating Officer} % Affiliation/role
{National University Technology Competition (NUTEC '19)} % Organization/group
{Peshawar, Pakistan} % Location
{Nov. 2018 - Feb. 2019} % Date(s)
{ % Description(s) of experience/contributions/knowledge
\begin{cvitems}
\begin{flushleft} \justifying
Established in 2009, The National University Technology Competition (NUTEC) is an inter - university, Student-run annual mega event. Over the years, it has achieved a status enviable prominence in the domain of higher education landscape of not only Khyber Pakhtunkhwa but across Pakistan. The Mega event is meticulously panned by a student body from Computer Science, Engineering and Management who are selected through a rigorous and competitive selection process.
\end{flushleft}
\end{cvitems}
}

\end{cventries}