%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Projects}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%-----------------------------------------------

\cventry
{Final Year Project - \textbf{Area of Specialization:} NLP, Machine Learning, Data Mining \& Web Programming } % Role
{Course Content Predictor Based on Industrial Trends } % Title
{Peshawar, Pakistan} % Location
{March. 2021} % Date(s)
{ % Description(s)
\begin{cvitems}
\item {Our Final Year Project introduces a forecasting system for the university elective courses. Utilizing forecasting models, our system forecast the student’s courses predicated on the most trending jobs for the Computer Science graduates in the IT industry. 
}
\end{cvitems}
}

%-----------------------------------------------


\cventry
{Semester Project - Machine Learning \& NLP } % Role
{Chatbot For Hospital Management System } % Title
{Peshawar, Pakistan} % Location
{Jan. 2021} % Date(s)
{ % Description(s)
\begin{cvitems}
\item {We build a chatbot using deep learning techniques. The chatbot are trained on the dataset which contains categories (intents), pattern and responses. We use a special recurrent neural network (LSTM) to classify which category the user’s message belongs to and then we will give a random response from the list of responses.
}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Team Lead Web \& IT} % Role
{\href{http://pwr.nu.edu.pk/acm/}{NUCES Peshawar ACM Student Chapter's Website}} % Title
{Peshawar, Pakistan} % Location
{Mar. 2020} % Date(s)
{ % Description(s)
\begin{cvitems}
\item {The Association for Computing Machinery is an international learned society for computing. NUCES Peshawar ACM Student Chapter is a non-profit organization established in 2010 at FAST-NU Peshawar. It is managed by the undergraduate student body from different academic years.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Lead Web Strategist} % Role
{NUTEC 2020, Signature Event Website} % Title
{Peshawar, Pakistan} % Location
{Oct. 2020} % Date(s)
{ % Description(s)
\begin{cvitems}
\item {The National University Technology Competition (NUTEC) is an inter-university, Student-run annual mega event. Over the years, it has achieved a status enviable prominence in the domain of higher education landscape of not only Khyber Pakhtunkhwa but across Pakistan.
}
\end{cvitems}
}

%------------------------------------------------

%------------------------------------------------

\cventry
{Web Designer} % Role
{\href{https://www.ingolsdigital.com/}{Ingols Digital, Company's Website}} % Title
{Vancouver, Canada} % Location
{Sep. 2019} % Date(s)
{ % Description(s)
\begin{cvitems}
\item {Ingols Digital is an online marketing company that helps businesses to generate revenue through the internet.They build affordable and fast websites that are extremely optimized from scratch so they can be ranked at the top pages of Search Engines.}
\end{cvitems}
}

%------------------------------------------------






\cventry
{Frontend Web Developer \& SEO Analyst  } % Role
{\href{http://icet.org.pk/2019}{ICET' 2019, International Conference Website}} % Title
{Peshawar, Pakistan} % Location
{Mar. 2019} % Date(s)
{ % Description(s)
\begin{cvitems}
\item {Designed, Developed \& Optimized the website of 15th International Conference on Emerging Technologies 2019, Conference hosted by FAST National University of Computer \& Emerging Sciences.
}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Semester Project - Java Based} % Role
{Food Ordering \& Management System} % Title
{Peshawar, Pakistan} % Location
{May. 2018} % Date(s)
{ % Description(s)
\begin{cvitems}
\item {It will be an application-based Food Ordering \& Management System which will be used by the Customer in a restaurant.
}
\end{cvitems}
}

%------------------------------------------------



\cventry
{Semester Project - Digital Logic Design } % Role
{Automated Car Parking Lot System} % Title
{Peshawar, Pakistan} % Location
{Oct. 2017} % Date(s)
{ % Description(s)
\begin{cvitems}
\item {Our demonstration facility presents a miniature model of an automated car parking system that regulates the number of cars that can be parked in a given space at any given time based on the parking space availability.
}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Semester Project - Data Structures (C++) } % Role
{Automated Bus Reservation System} % Title
{Peshawar, Pakistan} % Location
{Feb. 2017} % Date(s)
{ % Description(s)
\begin{cvitems}
\item {We the group of 2 members have developed an Online Bus Reservation System Project, this program have some features for Company which is providing bus services like they will install or set complete information about buses
}
\end{cvitems}
}

%------------------------------------------------

\end{cventries}

